% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Test},
  pdfauthor={Author Name},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[CO,CE]{This is fancy}
\fancyfoot[CO,CE]{So is this}
\fancyfoot[LE,RO]{\thepage}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Test}
\author{Author Name}
\date{July 29, 2020}

\begin{document}
\maketitle
\begin{abstract}
This is a pandoc test . . .
\end{abstract}

\hypertarget{Testing Sections}{%
\section{testing}\label{section}}

Can any help me find a list of all filehosts supported by JDownloader? Ideally I'd like just a list of file sharing sites where users can upload (mega.nz, 4shared, zippyshare, etc.) without all the content providers such as Youtube included, but if I have to curate the list I can do that.

I've looked high and low and can't find an answer to to this anywhere. I did find this thread: https://board.jdownloader.org/showthread.php?t=15153 where Community Manager pspzockerscene said to look in the source code for a list of file hosts. I'm happy to do that, and I followed all the instructions found at http://jdownloader.org/knowledge/wik...nt/get-started, but once I have Eclipse opened and all the code in front of me, I can't find the section of code that contains plugins for me to sort through. If someone can help me find that, that would also be quite helpful.

Can any help me find a list of all filehosts supported by JDownloader? Ideally I'd like just a list of file sharing sites where users can upload (mega.nz, 4shared, zippyshare, etc.) without all the content providers such as Youtube included, but if I have to curate the list I can do that.

I've looked high and low and can't find an answer to to this anywhere. I did find this thread: https://board.jdownloader.org/showthread.php?t=15153 where Community Manager pspzockerscene said to look in the source code for a list of file hosts. I'm happy to do that, and I followed all the instructions found at http://jdownloader.org/knowledge/wik...nt/get-started, but once I have Eclipse opened and all the code in front of me, I can't find the section of code that contains plugins for me to sort through. If someone can help me find that, that would also be quite helpful.

Can any help me find a list of all filehosts supported by JDownloader? Ideally I'd like just a list of file sharing sites where users can upload (mega.nz, 4shared, zippyshare, etc.) without all the content providers such as Youtube included, but if I have to curate the list I can do that.

I've looked high and low and can't find an answer to to this anywhere. I did find this thread: https://board.jdownloader.org/showthread.php?t=15153 where Community Manager pspzockerscene said to look in the source code for a list of file hosts. I'm happy to do that, and I followed all the instructions found at http://jdownloader.org/knowledge/wik...nt/get-started, but once I have Eclipse opened and all the code in front of me, I can't find the section of code that contains plugins for me to sort through. If someone can help me find that, that would also be quite helpful.

Can any help me find a list of all filehosts supported by JDownloader? Ideally I'd like just a list of file sharing sites where users can upload (mega.nz, 4shared, zippyshare, etc.) without all the content providers such as Youtube included, but if I have to curate the list I can do that.

I've looked high and low and can't find an answer to to this anywhere. I did find this thread: https://board.jdownloader.org/showthread.php?t=15153 where Community Manager pspzockerscene said to look in the source code for a list of file hosts. I'm happy to do that, and I followed all the instructions found at http://jdownloader.org/knowledge/wik...nt/get-started, but once I have Eclipse opened and all the code in front of me, I can't find the section of code that contains plugins for me to sort through. If someone can help me find that, that would also be quite helpful.

\hypertarget{testing subsection}{%
\subsection{sub testing}\label{subsection}}

\end{document}
